---
title: "Data_wrangling_2_review"
author: "Qingyue Zhuo qz2493"
date: "2022-10-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(httr)
```

### Extracting tables
#### load data from the web
read_html(url)
```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm" # copy-paste the link
drug_use_html = read_html(url) #read_html
drug_use_html
```

#### extracting tables from HTML
```{r}
drug_use_html %>%
  html_table()
```
here is the problem: the note at the bottom of each table appears in every column in the first row, we need to remove that
```{r}
table_marj = 
  drug_use_html %>%
  html_table() %>%
  first() %>% # table of the page
  slice(-1) # slice off the first row ?

table_marj
```

```{r}
table_marj_1 = 
  drug_use_html %>%
  html_table() %>%
  first() %>%
  slice(-2) # this will slice off the second row
```

```{r}
url_nyc = "https://www.bestplaces.net/cost_of_living/city/new_york/new_york"
table_nyc = 
  read_html(url_nyc) %>%
  html_table(header = TRUE) %>% # the head of the table if the head here, if not, the head after reading will be X1-Xn
  first() # first table of the page
```

### CSS Selector
```{r}
swm_html = read_html("https://www.imdb.com/list/ls070150896/")
```
The information is not stored in a handy table, we'll use CSS selector in html_elements() to extract the relavent HTML code, and convert it to text, and combine these into a dataframe
```{r}
title_vec = 
  swm_html %>%
  html_elements(".lister-item-header a") %>% #html_elements(."header")
  html_text()

gross_rev_vec = 
  swm_html %>%
  html_elements(".text-small:nth-child(7) span:nth-child(5)") %>%
  html_text()

runtime_vec = 
  swm_html %>%
  html_elements(".runtime") %>%
  html_text()

swm_df = 
  tibble(
    title = title_vec,
    rev = gross_rev_vec,
    runtime = runtime_vec
  ) # put everything you extract into a tibble
```

practice
```{r}
amazon_html = read_html("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1")

title_html = 
  amazon_html %>%
  html_elements(".a-text-bold span")%>%
  html_text()

review_html = 
  amazon_html %>%
  html_elements(".review-text-content span") %>%
  html_text()

stars_html = 
  amazon_html %>%
  html_elements("#cm_cr-review_list .review-rating") %>%
  html_text()

review = tibble(
  title = title_html,
  stars = stars_html,
  review = review_html
)
```
using an API
We can access the data directly using the API to improve reproducility and make it esier to update result to reflect new data
```{r}
nyc_water = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.csv") %>% #get+directory+csv
  content("parsed")
```
we can also import this data as a JSON file
```{r}
nyc_water =
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.json") %>% # get+directory+json
  content("text") %>%
  jsonlite::fromJSON() %>%
  as_tibble()
```

```{r}
brfss_smart2010 =
  GET("https://chronicdata.cdc.gov/resource/acme-vg9e.csv",
      query = list("$limit" = 5000)) %>%
  content("parsed")
      
```

